Project Description -- Erosion, Transport, Anomalous Diffusion, and Collapse in Granular and Porous Media

### 2019-11-18 docs/proposals/NSF/ProjDesc/ProjDesc.tex
NM

The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion~\cite{Quaife2018} in the Stokes flow regime, which is the regime relevant for the currently proposed applications of groundwater flow. Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion \cite{chi-moo-qua2019}.

>>>>

The PIs co-authored a paper in the {\em Journal of Computational Physics} describing numerical methods for simulating erosion~\cite{Quaife2018} in the Stokes flow regime, which is the regime relevant for the currently proposed groundwater applications. Very recently the PIs, along with postdoctoral scholar Shang-Huan Chiu, submitted a second paper on newly developed methods for precise characterization of transport and dispersion within the special class of porous-media configurations formed by erosion \cite{chi-moo-qua2019}.
